Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-21 Article.tex
Update of whole Article concerning plastic strain

\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
\newcommand{\RMSE}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \text{s}^{-1} - 5\ \text{s}^{-1}$) and temperatures ($1050\celsius-1250\celsius$). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot\varepsilon^p = 0.01\ \text{s}^{-1}$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon^p = 0.1\ \text{s}^{-1}$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon^p$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
\end{abstract}

@@

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\text{s}^{-1}$, $0.01~\text{s}^{-1}$, $0.1~\text{s}^{-1}$, $1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$ and $5.0~\text{s}^{-1}$.

@@

The set of flow stress $\sigma^y$ versus plastic strain $\varepsilon^p$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon^p$ but decreases with increasing temperature $T$.
It should be noted that the plastic strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon^p$, the flow stress $\sigma^y$ increases with the plastic strain $\varepsilon^p$ until a value of about $\varepsilon^p=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\text{s}^{-1}$, $2.0~\text{s}^{-1}$, and $5.0~\text{s}^{-1}$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

@@

The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon^p$, strain rate $\mdot\varepsilon^p$, and temperature $T$.
However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon^p$, $\mdot\varepsilon^p$ and $T$) separately as a factor in the mathematical expression of the model.
Hence its inability to describe the phenomenon of softening induced by temperature.
The equation that describes this model is given as follows \cite{Johnson-1983}:

\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon^p}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $\sigma^y$ is the flow stress, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.

For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\text{s}^{-1}$ and $T_0=1050\celsius$ respectively.

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=(11.758$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=25.563$~MPa and $n=0.139$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.338$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.730$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.

@@

%-------------------------------------------------------------------------
\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------
\OP{This introduction paragraph is entirely copied from the WJET publication}
As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon^p=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon^p$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon^p}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon^p/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\OP{Are you absolutely sure that the HS model takes into account the plastic strain $\varepsilon^p$ and not the strain $\varepsilon$ ? I don't think that it is the plastic strain, so I changed the mathematical expression of $\sigma^y$}
The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in finite element simulation software, although the determination of its parameters is easier than that of the JC or MZA model. 
The programming of a simple identification script is sufficient to identify its parameters for a given material. 
The equation of the HS model is given by the following relation:
\begin{equation}
\sigma^y = A~e^{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~e^{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~e^{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}\label{eq:HS}
\end{equation}
where $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier. 
The coefficients $A$ and $m_i$ are the parameters of the model to be identified. 
However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification. 
For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only by truncating its expression according to the number of parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.

@@

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS}. 
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important. 
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate. 
The DRX phenomena cannot be reproduced by this type of model.

@@

The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material. Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon^p$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation. This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature. The following equations describe the Arrhenius model.

@@

\mdot\varepsilon^p = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)

@@

\mdot\varepsilon^p = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)

@@

\mdot\varepsilon^p = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)

@@

Where $\mdot\varepsilon^p$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:

@@

Z = \mdot\varepsilon^p\exp\left(\frac{Q}{RT}\right)

@@

\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon^p -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}

@@

\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon^p - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}

@@

From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon^p)$  and $\sigma^y = f(\ln\mdot\varepsilon^p)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$. It should be noted that later in this document all values of strain will be taken into account.

@@

\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon^p  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}

@@

Q = R\left[\frac{\partial \ln \mdot\varepsilon^p}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon^p}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}

>>>>

\newcommand{\dotp}{\boldsymbol{\cdot}}
%\newcommand{\ccirc}{\kern0.5ex\vcenter{\hbox{$\scriptstyle\circ$}}\kern0.5ex}
\newcommand{\e}[1]{\exp\left({#1}\right)}
\newcommand{\lay}[1]{^{(#1)}}
\newcommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\newcommand*{\ie}{\emph{i.e.}\@\xspace}
\newcommand*{\versus}{\emph{vs.}\@\xspace}
\newcommand*{\eal}{et \emph{al.}\@\xspace}
\newcommand*{\eg}{e.g.,\@\xspace}
\newcommand{\RMSE}{\text{E}_\text{RMS}}
\newcommand{\AARE}{\text{E}_\text{AAR}}
\newcommand{\R}{\text{R}}
\newcommand{\ps}{\text{s}^{-1}}
%\newcommand{\Dev}	{\mbox{\Large\ensuremath{\mathsf{s}}}}
%\DeclareMathOperator{\sech}{sech}
%\DeclareMathOperator{\sigmoid}{sig}

@@

\begin{abstract}
The high-temperature deformation behavior of the AISI P20 alloy was investigated by performing hot compression tests over a wide range of strains ($0.025 - 0.7$),  strain rates ($0.001\ \ps - 5\ \ps$) and temperatures ($1050\celsius-1250\celsius$). Based on the experimental data (stress-strain curves), empirical models as the Johnson-Cook (JC), Modified-Zerilli-Armstrong (MZA), Hansel-Spittel (HS), Arhenius (AR) and PTM on the one hand and an ANN model on the other hand were developed to predict the flow behavior of this alloy. Then, a comparative study between the analytical models and the ANN model was carried out on the basis of the calculation of some coefficients allowing to test the efficiency of each model. These coefficients are the correlation coefficient $R$, the Average Absolute  Relative Error $\AARE$ and the Root Mean Square Error ($\RMSE$). From these parameters it was found that the JC, MZA and HS models are not suitable for predicting the behavior of AISI P20 alloy whereas the AR and PTM models can be used for most strain rates to predict the flow behavior of this alloy. For the strain rate ($\mdot\varepsilon = 0.01\ \ps$)  the AR model fails to describe the flow for temperatures $1050\celsius$ and $1100\celsius$  while in the case of the PTM model, the strain rate  ($\mdot\varepsilon = 0.1\ \ps$) is not well described. This is due to the fact that this model is a sequence of polynomials which can create oscillations if the degree is high. Regarding the ANN model, the architecture retained is composed of two hidden layers of which the first hidden layer contains $15$ neurons and the second contains $7$ neurons and the input layer contains $3$ neurons corresponding to the strain ($\varepsilon^p$), strain rate ($\mdot\varepsilon$) and temperature ($T$) and the output layer contains a single neuron corresponding to the flow stress ($\sigma^y$). The results of the ANN model show a very good agreement between the predictions and the experiment. This demonstrates that this  formulation of constitutive law exceeds highly the analytical models in terms of prediction. To validate the performance of these models their capacities to interpolate and extrapolate the data were also tested where all the models relatively prove a good interpolation capacity whereas this is not the case for extrapolation where only the AR, PTM and ANN models are acceptable but still mentioning that the ANN model remains the best in both interpolation and extrapolation.
\end{abstract}

@@

The material used in this study is the modified carbon alloy AISI P20 whose chemical composition is given in Table \ref{tab:Composition}.
Cylindrical samples were machined with an initial diameter of $10$~mm and a height of $15$~mm.
A batch of $30$ hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for the five temperature levels of $1050\celsius$, $1100\celsius$, $1150\celsius$, $1200\celsius$ and $1250\celsius$ with the six strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1.0~\ps$, $2.0~\ps$ and $5.0~\ps$.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition ($6$ strain rates and $5$ temperatures) is presented in Figure \ref{fig:rawData}.
\OP{It is necessary to give indications concerning the structure of the data: how many points, what amplitude of deformation,...} The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1.0~\ps$, $2.0~\ps$, and $5.0~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

@@

The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model.
Hence its inability to describe the phenomenon of softening induced by temperature.
The equation that describes this model is given as follows \cite{Johnson-1983}:

\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The other values are reference ones, so that $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.

For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$ respectively.

The procedure used for the determination of the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows obtaining one after the other the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate and reference temperature is $A=11.758$~MPa.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, it is then possible to determine these two constants by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=25.563$~MPa and $n=0.139$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering all the curves at $T=T_0$ then gives $C=0.338$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from the knowledge of the previous and gives $m=0.730$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JCparams}.

@@

%-------------------------------------------------------------------------
\subsection{Modified Zerilli-Armstrong model\label{sec:MZA}}
%-------------------------------------------------------------------------
\OP{This introduction paragraph is entirely copied from the WJET publication}
As mentioned earlier, Johnson-Cook's law, widely used in the scientific community and implemented as a base in the Abaqus FEM code, is an empirical model for which the effects of strain, strain rate, and temperature on material behavior are considered separately.
Since a coupling exists in reality between these three variables, it is preferable to opt for a Zerilli-Armstrong (ZA) model \cite{Hull-2011}.
But the original for of ZA model has some limitations due to the fact that it is considered as two terms and to ameliorate that formulation Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right]
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material. The formulation of the model can be found in \cite{Samantaray-2009} and determination of its parameters is sumarized as following.

Considering the expression of the model given by Equation (\ref{eq:MZA-model}), parameter $C_1$ is deduced direcly from $\sigma^y(\varepsilon^p=0,T=T_0,\mdot\varepsilon=\mdot{\varepsilon}_0)$. When the current strain rate $\mdot\varepsilon$ is identical to the reference strain rate $\mdot{\varepsilon}_0$, the Equation (\ref{eq:MZA-model}) becomes :
\begin{equation}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)\right]
\end{equation}
Taking the logarithm of the previous relationship we have :
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right)-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right)
\end{equation}
By plotting the function $\ln\sigma^y\left(T-T_0\right)$ the y-intercept and the slope of this line can be deduced as $I_1=\ln\left(C_1+C_2\varepsilon^{p^n}\right)$ and $S_1=-\left(C_3+C_4\varepsilon^p\right)$.
From the expression of $I_1$ we can write:
\begin{equation}
\ln\left(\exp(I_1)-C_1\right) = \ln C_2+n\ln\varepsilon^p
\end{equation}
By plotting the function $\ln\left(\exp(I_1)-C_1\right)$ versus $\ln\varepsilon^p$ we can deduce $n$ and $C_2$. The plot of $S_1$ versus $\varepsilon^p$ allows deducing $C_3$ and $C_4$ from the y-intercept and the slope, respectively. Once the first four terms of the model are calculated, we can now take the logarithm of the entire MZA model given by Equation (\ref{eq:MZA-model}).
\begin{equation}
\ln\sigma^y = \ln\left(C_{1}+C_{2}\varepsilon^{p^n}\right) - \left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + S_2\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)
\end{equation}
with $S_2=C_5+C_6\left(T-T_0\right)$. Finally, the graph $\ln\sigma^y$ versus $ \ln(\mdot\varepsilon/\mdot{\varepsilon}_0)$ allows deducing $C_5$ and $C_6$ from the slope $S_2$. The parameters of MZA model are given in the Table \ref{tab: MZAparameters} while its prediction are shown in Figure \ref{fig:iCorrelationMZA}. It can be seen from those figures that the MZA model as JC model is not suitable to describe experimental at low strain rates but much better for high strain rates. The deviation between the predicted values and the experimental values is large because this model has problem to correctly describe the softening in its formulation. That is aspect of the limitations of that model as presented in \cite{TizeMha-2022}.
\begin{table}[h!]
\centering{}
\caption{Parameters' constants of Modified-Zerilli-Armstrong Model}
\begin{tabular}{lllllllc}
\hline
&         &             &		   &		 &			   &&\\
Parameters&$C_1(\text{MPa})$    &$C_2(\text{MPa})$        & $C_3(\times10^{-5})$     & $C_4(\times10^{-5})$   & $C_5(\times10^{-5})$       &$C_6(\times10^{-5})$&$n$\\
&         &             &		   &	     &	           &&\\
\hline
Values&$43.0988$&$112.975$& $330.976$&$4.27581$&$14106.3$&$17.4178$&$0.305028$\\
\hline
\label{tab: MZAparameters}
\end{tabular}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=1.02\columnwidth]
{Figures/CompExpMZA}
\caption{Comparison between the experimental and predicted flow stresses by MZA model}
\label{fig:iCorrelationMZA}
\end{figure}
\FloatBarrier

@@

\OP{Are you absolutely sure that the HS model takes into account the plastic strain $\varepsilon^p$ and not the strain $\varepsilon$ ? I don't think that it is the plastic strain, so I changed the mathematical expression of $\sigma^y$}
The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in finite element simulation software, although the determination of its parameters is easier than that of the JC or MZA model. 
The programming of a simple identification script is sufficient to identify its parameters for a given material. 
The equation of the HS model is given by the following relation:
\begin{equation}
\sigma^y = A~e^{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~e^{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~e^{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}\label{eq:HS}
\end{equation}
where $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature as proposed earlier. 
The coefficients $A$ and $m_i$ are the parameters of the model to be identified. 
However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification. 
For its identification, several authors restrict its expression to a reduced number of $5$ or $6$ $m_i$ parameters only, by forcing a zero value for the other parameters \cite{Chadha-2018, Rudnytskyj-2020, Mehtedi-2015}.

@@

The comparison of the values predicted by the HS model and the experimental values is presented in Figure \ref{fig:iCorrelationHS} where the dots represent the experimental values and the solid lines are the values predicted by the HS flow law. 
It appears that this model as well as the previous ones do not predict well the experimental one and the difference is relatively important for all strain rates below $1.0~\ps$. 
This shows that this model is not appropriate for the characterization of this alloy, in particular because of the strong non-linearity of the behavior for low values of the strain rate. 
The DRX phenomena cannot be reproduced by this type of model.

@@

The Arrhenius tye model is one of the most widely used models, especially when it comes to studying the microstructure of the material. Indeed, this model takes into account the physical phenomena that describe the behavior of the material and also the relations between stress ($\sigma^y$), strain ($\varepsilon^p$), the strain rate ($\mdot\varepsilon$) and the temperature ($T$) could be expressed in form of the power law, the exponential law and the hyperbolic sine type equation. This facilitates an easier description of the phenomenon of softening observed in material due to the increase in temperature. The following equations describe the Arrhenius model.

@@

\mdot\varepsilon = A_1\sigma^{y^{n_1}}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y < 0.8)

@@

\mdot\varepsilon = A_2\exp(\beta\sigma^y)\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~\alpha\sigma^y > 1.2)

@@

\mdot\varepsilon = A_3\left[\sinh(\alpha\sigma^y)\right]^{n_2}\exp\left(-\frac{Q}{RT}\right) \qquad (for ~~all\ \sigma^y)

@@

Where $\mdot\varepsilon$ is the strain rate ($s^{-1}$), $Q$ is the deformation activation energy ($KJmol^{-1}$), $R$ is the universal gas constant ($8.314\ J mol^{-1} K^{-1}$), $T$ is the absolute temperature ($K$) and $A_1, A_2, A_3, n_1$, $n_2, \beta$ and $\alpha(\beta/n_1)$ are the material constants. To take into account the effects of temperature and strain rate on the deformation, a parameter ($Z$) called Zener-Hollomon parameter is introduced whose expression is given as follows:

@@

Z = \mdot\varepsilon\exp\left(\frac{Q}{RT}\right)

@@

\ln \sigma^y = \frac{1}{n_1}\ln \mdot\varepsilon -\frac{1}{n_1}\ln A_1 +  \frac{1}{n_1}\frac{Q}{RT}

@@

\sigma^y = \frac{1}{\beta}\ln \mdot\varepsilon - \frac{1}{\beta}\ln A_2 + \frac{1}{\beta}\frac{Q}{RT}

@@

From these two equations, we can easily deduce the parameters $n_1$ and $\beta$ as the slopes of the functions $\ln\sigma^y = f(\ln\mdot\varepsilon)$  and $\sigma^y = f(\ln\mdot\varepsilon)$ as shown in Figure \ref{fig:LnAlp} and Figure \ref{fig:LnSinhE0} for $\varepsilon^p = 0.1$. It should be noted that later in this document all values of strain will be taken into account.

@@

\ln\sinh(\alpha\sigma^y) = \frac{1}{n_2}\ln \mdot\varepsilon  -  \frac{1}{n_2}\ln A_3 + \frac{1}{n_2} \frac{Q}{RT}

@@

Q = R\left[\frac{\partial \ln \mdot\varepsilon}{\partial \ln [\sinh(\alpha\sigma^y)]}\right]_{T}\left[\frac{\partial \ln [\sinh(\alpha\sigma^y)]}{\partial (1/T)}\right]_{\mdot\varepsilon}= Rn_2\frac{d\left\{\ln\left[\sinh(\alpha\sigma^y)\right]\right\}}{d(1/T)}
